Planar Maximal Covering with Ellipses

### 2019-05-07 quali/quali.presentation/slides.tex
WIP

		\item It can be implemented in $K\log{n}$ where $K$ is the number of intersections \autocite{bentley:1979}.

@@

		\item As it was mentioned, the solution found by this algorithm is a solution for the Maximal Covering by One Disk.
	\end{itemize}

@@

	\begin{block}{Ellipse}
		Given a center $c \in \R^2$ and $Q \in \R^ {2x2}$, an ellipse is the set of points that satisfy

@@

	\begin{block}{Axis-parallel ellipse}
		Any $2$ by $2$ diagonal d.p. matrix determines an axis-parallel ellipse, which can also be described by

@@

\begin{frame}[fragile]{Maximal Covering by Ellipses}{Pre-processing that finds every possible coverage for ellipse $E_i$}
	\begin{algorithm}[H]
		\caption{Adaptation of the algorithm for one disk to produce a candidate list for every ellipse.}\label{algoritmo:mce1}
		\begin{algorithmic}[1]
			\STATE $A \gets \bigcup_{j \in I_i} \{\Gamma_+(i,j) \cup \Gamma_-(i,j)\}$
			\STATE $Z \gets \{\}$
			\STATE $Cov \gets \{p_i\}$
			\FOR{$cnt=1..2$} 
			\FOR{$a \in A$}
			\STATE Let $p_a$ be the point that intersects $E_i$ at angle $a$. 
			\IF{$a$ is a starting angle}
			\STATE $Cov \gets Cov \cup \{p_a\}$
			\ELSE
			\STATE $Cov \gets Cov \setminus \{p_a\}$
			\ENDIF
			\STATE $Z \gets Z \cup \{Cov\}$
			\ENDFOR
			\ENDFOR

@@

\begin{frame}{Maximal Covering by Ellipses}{$m$ Ellipses}
	The modified one-disk-cover algorithm produces a list of candidates of location for each ellipse. An optimal solution is guaranteed to be in this list.
\end{frame}

>>>>

		\item It can be implemented in $\bigO(K\log{n})$ where $K$ is the number of intersections \autocite{bentley:1979}.

@@

	\end{itemize}
	As it was mentioned, the solution found by this algorithm is a solution for the Maximal Covering by One Disk.

@@

	\begin{block}{Ellipse}
		Given a center $c \in \R^2$ and $Q \in \R^ {2x2}$ a positive definite matrix, an ellipse is the set of points that satisfy

@@

	\begin{block}{Axis-parallel ellipse}
		Any $2$ by $2$ diagonal p.d. matrix determines an axis-parallel ellipse, which can also be described by

@@

\begin{frame}[fragile]{Maximal Covering by Ellipses}{The algorithm for $m$ ellipses}
	\begin{algorithm}[H]
		%\caption{Adaptation of the algorithm for one disk to produce a candidate list for every ellipse.}\label{algoritmo:mce1}
		\begin{algorithmic}[1]
			\FOR{$E_i \in \E$}
				\STATE{Fix an ellipse with the same shape as $E_i$ at each point.}
				\STATE{$Z_i \gets $ every solution of Maximum Weight Clique for it.}
			\ENDFOR
		\end{algorithmic}
	\end{algorithm}
\begin{algorithm}[H]
	\begin{algorithmic}[1]

			\STATE{\textbf{function} $f(\Pp, j)$}

				\IF{$j=m$}{
					\RETURN 0
				}
				\ENDIF
				\STATE{$ans \gets 0$}
				\FOR{$z \in Z_j$}
					\STATE{Fix $E_j$ at $z$}
					\STATE{$Q \gets$ points covered by $E_j(z)$}
					\STATE{$ans \gets \max\{ans,f(\Pp \setminus Q, j+1) + w(Q)\}$}
				\ENDFOR
				\RETURN{$ans$}

			%\FOR{$p_i \in \Pp$}
			%\STATE $A \gets \bigcup_{j \in I_i} \{\Gamma_+(i,j) \cup \Gamma_-(i,j)\}$
			%\STATE $Z \gets \{\}$
			%\STATE $Cov \gets \{p_i\}$
			%\FOR{$cnt=1..2$} 
			%\FOR{$a \in A$}
			%\STATE Let $p_a$ be the point that intersects $E_i$ at angle $a$. 
			%\IF{$a$ is a starting angle}
			%\STATE $Cov \gets Cov \cup \{p_a\}$
			%\ELSE
			%\STATE $Cov \gets Cov \setminus \{p_a\}$
			%\ENDIF
			%\STATE $Z \gets Z \cup \{Cov\}$
			%\ENDFOR
			%\ENDFOR
			%\ENDFOR

@@

%\begin{frame}{Maximal Covering by Ellipses}{$m$ Ellipses}
%	The modified one-disk-cover algorithm produces a list of candidates of location for each ellipse. An optimal solution is guaranteed to be in this list.
%\end{frame}
